---
title: "psymetadata: Memory Suppression example"
author: "Martyna Citkowicz"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


```{r}
library(metaselection)
library(metadat)
library(psymetadata)
library(metafor)
library(tidyverse)
library(here)
devtools::load_all()

```

# Memory Suppression Meta-analysis
```{r}
dat_ex <- stramaccia2021

dat_ex <- dat_ex |>
  rename(esid = es_id, studyid = study_id) |>
  mutate(
    d = yi,
    Va = vi,
    Var_d = Va,
    sd_d = sqrt(Var_d),
    var_d = Var_d,
    p_onesided = 1 - pnorm(d / sd_d)
  )

length(unique(dat_ex$studyid)); length(unique(dat_ex$esid))
```

# Mean Only

## Unadjusted estimate: mean only
```{r}
ex_unadj_mean <- rma.uni(
  data = dat_ex,
  yi = d,
  sei = sd_d,
  method = "ML"
)
ex_unadj_mean

ex_unadj_mean_cil <- ex_unadj_mean$tau2 - 1.96*ex_unadj_mean$se.tau2
ex_unadj_mean_ciu <- ex_unadj_mean$tau2 + 1.96*ex_unadj_mean$se.tau2
ex_unadj_mean_cil; ex_unadj_mean_ciu
```

## Forest plot
```{r}
funnel(ex_unadj_mean, refline = 0, level = c(90, 95, 99))
```

## CHE estimate: mean only
```{r}
V_mat <- vcalc(
    vi = vi, 
    cluster = studyid,
    obs = esid, 
    data = dat_ex,
    rho = 0.5,
    sparse = TRUE
  )

ex_che <- rma.mv(yi = yi,
                  V = V_mat,
                  random = ~ 1 | studyid / esid, 
                  data = dat_ex, 
                  sparse = TRUE, 
                  digits = 3) |> 
    robust(cluster = studyid, clubSandwich = TRUE)

ex_che
```

## Adjusted estimate in metaselection: Beta model mean only
```{r}
ex_adj_ms_beta_mean <- selection_model(
  dat = dat_ex,
  yi = d,
  sei = sd_d,
  pi = p_onesided,
  cluster = studyid,
  selection_type = "beta",
  steps = c(.025,.975),
  make_sandwich = TRUE
)
ex_adj_ms_beta_mean
```

## Selection plot: Beta model mean only
```{r}
selection_plot(ex_adj_ms_beta_mean)
```

## Adjusted estimate in metaselection: Step 3PSM model mean only
```{r}
ex_adj_ms_step3_mean <- selection_model(
  dat = dat_ex, 
  yi = d,
  sei = sd_d,
  cluster = studyid,
  selection_type = "step",
  steps = 0.025
)

ex_adj_ms_step3_mean
```

## Selection plot: Step 3 PSM model mean only
```{r}
selection_plot(ex_adj_ms_step3_mean)
```

## Adjusted estimate in metaselection: Step 4PSM model mean only
```{r}
ex_adj_ms_step4_mean <- selection_model(
  dat = dat_ex, 
  yi = d,
  sei = sd_d,
  cluster = studyid,
  selection_type = "step",
  steps = c(0.025, .5)
)

ex_adj_ms_step4_mean
```

## Selection plot: Step 4PSM model mean only
```{r}
selection_plot(ex_adj_ms_step4_mean)
```

# Moderator

## Unadjusted estimate: moderator
```{r}
ex_unadj_mod <- rma.uni(
  data = dat_ex,
  yi = d,
  sei = sd_d,
  method = "ML",
  mods = ~ stimuli
)
ex_unadj_mod

ex_unadj_mod_cil <- ex_unadj_mod$tau2 - 1.96*ex_unadj_mod$se.tau2
ex_unadj_mod_ciu <- ex_unadj_mod$tau2 + 1.96*ex_unadj_mod$se.tau2
ex_unadj_mod_cil; ex_unadj_mod_ciu
```

## Adjusted estimate in metaselection: Beta model moderator
```{r}
ex_adj_ms_beta_mod <- selection_model(
  dat = dat_ex,
  yi = d,
  sei = sd_d,
  pi = p_onesided,
  cluster = studyid,
  selection_type = "beta",
  steps = c(.025,.975),
  make_sandwich = TRUE,
  mean_mods = ~ stimuli
)
ex_adj_ms_beta_mod
```

## Selection plot: Beta model moderator
```{r}
selection_plot(ex_adj_ms_beta_mod)
```

## Adjusted estimate in metaselection: Step 3PSM model moderator
```{r}
ex_adj_ms_step3_mod <- selection_model(
  dat = dat_ex, 
  yi = d,
  sei = sd_d,
  cluster = studyid,
  selection_type = "step",
  steps = 0.025,
  mean_mods = ~ stimuli
)

ex_adj_ms_step3_mod
```

## Selection plot: Step 3 PSM model moderator
```{r}
selection_plot(ex_adj_ms_step3_mod)
```

## Adjusted estimate in metaselection: Step 4PSM model moderator
```{r}
ex_adj_ms_step4_mod <- selection_model(
  dat = dat_ex, 
  yi = d,
  sei = sd_d,
  cluster = studyid,
  selection_type = "step",
  steps = c(0.025, .5),
  mean_mods = ~ stimuli
)

ex_adj_ms_step4_mod
```

## Selection plot: Step 4PSM model moderator
```{r}
selection_plot(ex_adj_ms_step4_mod)
```
