---
title: "SREE 2024: Science example"
author: "Martyna Citkowicz"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


```{r}
library(metaselection)
library(metadat)
library(metafor)
library(tidyverse)
library(here)
devtools::load_all()

```

# Science Meta-analysis
```{r}
sci <- read_csv(here('tests/testdata','ScienceMeta.csv'))

sci <- sci |>
  rename(esid = es_id, studyid = study_id) |>
  mutate(
    d = yi,
    Va = vi,
    Var_d = Va,
    sd_d = sqrt(Var_d),
    var_d = Var_d,
    p_onesided = 1 - pnorm(d / sd_d)
  )
```

# Unadjusted estimate: mean only
```{r}
sci_unadj_mean <- rma.uni(
  data = sci,
  yi = d,
  sei = sd_d,
  method = "ML"
)
sci_unadj_mean

sci_unadj_mean_cil <- sci_unadj_mean$tau2 - 1.96*sci_unadj_mean$se.tau2
sci_unadj_mean_ciu <- sci_unadj_mean$tau2 + 1.96*sci_unadj_mean$se.tau2
sci_unadj_mean_cil; sci_unadj_mean_ciu
```

# Forest plot
```{r}
funnel(sci_unadj_mean, refline = 0, level = c(90, 95, 99))
```

# Unadjusted estimate: moderator
```{r}
sci_unadj_mod <- rma.uni(
  data = sci,
  yi = d,
  sei = sd_d,
  method = "ML",
  mods = ~ outcome_type_author
)
sci_unadj_mod

sci_unadj_mod_cil <- sci_unadj_mod$tau2 - 1.96*sci_unadj_mod$se.tau2
sci_unadj_mod_ciu <- sci_unadj_mod$tau2 + 1.96*sci_unadj_mod$se.tau2
sci_unadj_mod_cil; sci_unadj_mod_ciu
```

# Adjusted estimate in metafor: Beta model
```{r}
sci_adj_mf <- selmodel(
  x = sci_unadj_mod,
  type = "beta",
  steps = c(0.025, 0.975),
  control=list(optimizer="nlminb"),
  #verbose = "TRUE"
)
sci_adj_mf

sci_adj_mf_cil <- sci_adj_mf$tau2 - 1.96*sci_adj_mf$se.tau2
sci_adj_mf_ciu <- sci_adj_mf$tau2 + 1.96*sci_adj_mf$se.tau2
sci_adj_mf_cil; sci_adj_mf_ciu
```

# Adjusted estimate in metaselection: Beta model mean only
```{r}
sci_adj_ms_mean <- selection_model(
  dat = sci,
  yi = d,
  sei = sd_d,
  pi = p_onesided,
  cluster = studyid,
  selection_type = "beta",
  steps = c(.025,.975),
  make_sandwich = TRUE
)
sci_adj_ms_mean
```

# Selection plot: Beta model mean only
```{r}
selection_plot(sci_adj_ms_mean)
```

# Adjusted estimate in metaselection: Beta model moderator
```{r}
sci_adj_ms_mod <- selection_model(
  dat = sci,
  yi = d,
  sei = sd_d,
  pi = p_onesided,
  cluster = studyid,
  selection_type = "beta",
  steps = c(.025,.975),
  make_sandwich = TRUE,
  mean_mods = ~ outcome_type_author
)
sci_adj_ms_mod
```

# Selection plot: Beta model moderator
```{r}
selection_plot(sci_adj_ms_mod)
```

# CHE estimate
```{r}
V_mat <- vcalc(
    vi = vi, 
    cluster = studyid,
    obs = esid, 
    data = sci,
    rho = 0.5,
    sparse = TRUE
  )

sci_che <- rma.mv(yi = yi,
                  V = V_mat,
                  random = ~ 1 | studyid / esid, 
                  data = sci, 
                  sparse = TRUE, 
                  digits = 3) |> 
    robust(cluster = studyid, clubSandwich = TRUE)

sci_che
```

# Adjusted estimate in metaselection: Step 3PSM model
```{r}
sci_adj_ms_step3 <- selection_model(
  dat = sci, 
  yi = d,
  sei = sd_d,
  cluster = studyid,
  selection_type = "step",
  steps = 0.025
)

sci_adj_ms_step3
```

# Selection plot: Step 3 PSM model
```{r}
selection_plot(sci_adj_ms_step3)
```

# Adjusted estimate in metaselection: Step 4PSM model
```{r}
sci_adj_ms_step4 <- selection_model(
  dat = sci, 
  yi = d,
  sei = sd_d,
  cluster = studyid,
  selection_type = "step",
  steps = c(0.025, .5)
)

sci_adj_ms_step4
```

# Selection plot: Step 4PSM model
```{r}
selection_plot(sci_adj_ms_step4)
```
