---
output: github_document
bibliography: vignettes/references.bib
editor_options: 
  markdown: 
    wrap: sentence
---

<!-- badges: start -->

[![R-CMD-check](https://github.com/jepusto/metaselection/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jepusto/metaselection/actions/workflows/R-CMD-check.yaml) [![Codecov Status](https://codecov.io/gh/jepusto/metaselection/graph/badge.svg?token=8T7IUFT1QV)](https://codecov.io/gh/jepusto/metaselection) 
<!-- [![CRAN Version](http://www.r-pkg.org/badges/version/metaselection)](https://CRAN.R-project.org/package=metaselection) -->
<!-- [![](http://cranlogs.r-pkg.org/badges/grand-total/metaselection)](https://CRAN.R-project.org/package=metaselection) -->
<!-- [![](http://cranlogs.r-pkg.org/badges/last-month/metaselection)](https://CRAN.R-project.org/package=metaselection) -->

<!-- badges: end -->

# metaselection

Selective reporting is a major concern for research syntheses because it distorts the evidence base available for a meta-analysis. There are many tools available to investigate and correct for selective reporting but few of them can accommodate dependent effect sizes.
Ignoring the dependency of effect size estimates included in a meta-analysis leads to overly narrow confidence intervals, hypothesis tests with inflated Type 1 error rates, and incorrect inferences.

[@pustejovsky2025estimation](https://osf.io/preprints/metaarxiv/qg5x6_v4) and [@citkowicz2026estimating](https://osf.io/preprints/metaarxiv/wjpxk_v1) developed methods for investigating and accounting for selective reporting in meta-analytic models that also account for dependent effect sizes.
Their simulation results show that using a marginal selection model reduces bias in the estimate of the overall effect size compared to using conventional summary meta-analysis models or techniques such as the PET/PEESE adjustment.
Moreover, combining the marginal selection model with cluster bootstrapping --- particularly the two-stage cluster bootstrapping --- leads to confidence intervals with close-to-nominal coverage rates.

The `metaselection` package provides an implementation of the methods proposed and evaluated by @pustejovsky2025estimation and @citkowicz2026estimating.
The main function, [`selection_model()`](https://jepusto.github.io/metaselection/reference/selection_model.html), can fit step- and beta-function selection models.
To handle dependence in the effect size estimates, the function provides options to use cluster-robust (sandwich) variance estimation or cluster bootstrapping to assess uncertainty in the model parameter estimates. We highly recommend using cluster bootstrapping, particularly the two-stage cluster bootstrapping with percentile bootstrap confidence intervals. 

## Installation

You can install the development version of the package, along with a vignette demonstrating how to use it, from GitHub with:

```{r, eval = FALSE}
# If not already installed, first run install.packages("remotes")

remotes::install_github("jepusto/metaselection", dependencies = TRUE, build_vignettes = TRUE)
```

It may take a few minutes to install the package and vignette.
Setting `build_vignettes = FALSE` will lead to faster installation, although it will preclude viewing the package vignette.

After installation, you can view the vignette by running the command:

```{r, eval = FALSE}
vignette("selection-models", package = "metaselection")
```

You can also [view the vignette online](https://jepusto.github.io/metaselection/articles/selection-models.html) on the `metaselection` package website.

## Example

The following example uses data from a meta-analysis by @lehmann2018meta which examined the effects of color red on attractiveness judgments.
The dataset is included in the `metadat` package [@metadat] as `dat.lehmann`.
In the code below, we fit a three-parameter step-function selection model to the Lehmann dataset using the `selection_model()` function, with confidence intervals computed using two-stage cluster bootstrapping. Additionally, we use a default set of weak priors to regularize the estimates (for detail, see [`define_priors()`](https://jepusto.github.io/metaselection/reference/define_priors.html)). The function also has an argument that can be used to set the direction of the alternative hypothesis used in computing the p-values (default `alternative = "greater"`).
For further details on how to use the `selection_model()` function, please see the [vignette](https://jepusto.github.io/metaselection/articles/selection-models.html).


```{r 3PSM_boot, warning = FALSE, message = FALSE}
library(metaselection)

data("dat.lehmann2018", package = "metadat")
dat.lehmann2018$study <- dat.lehmann2018$Full_Citation
dat.lehmann2018$sei <- sqrt(dat.lehmann2018$vi)

set.seed(20240910)

mod_3PSM_boot <- selection_model(
  data = dat.lehmann2018, 
  yi = yi,
  sei = sei,
  cluster = study,
  selection_type = "step",
  steps = .025,
  priors = define_priors(),
  alternative = "greater",
  CI_type = "percentile",
  bootstrap = "two-stage",
  R = 19
  # Set R to a much higher number of bootstrap replications, 
  # such as 1999, to obtain confidence intervals with 
  # more accurate coverage rates
)

summary(mod_3PSM_boot)
```

The beta estimate of `r round(mod_3PSM_boot$est["beta","Est"], 3)`, with a 95% confidence interval of [`r round(mod_3PSM_boot$est["beta","percentile_lower"], 3)`, `r round(mod_3PSM_boot$est["beta","percentile_upper"], 3)`], represents the overall average effect after accounting for both selection bias and dependent effects.
The `tau2` ($\tau^2$) estimate of `r round( exp(mod_3PSM_boot$est["gamma","Est"]), 3)` is the estimated total variance, including both between- and within-study heterogeneity.
`lambda1` ($\lambda_1$) is the selection parameter.
The estimate of `r round(exp(mod_3PSM_boot$est["zeta1","Est"]), 3)` indicates that effect size estimates with one-sided $p$-values greater than 0.025 are only about half as likely to be reported as estimates that are positive and statistically significant (i.e., estimates with $p < 0.025$).
[This infographic](https://www.air.org/sites/default/files/2025-09/How-to-Read-Step-Function-Selection-Model-Results-infographic-Sept-2025.pdf) provides further guidance on interpreting the model output.
<!--# QUESTION: Do you want to move this infographic to our package website as a separate vignette so we don't have to rely on AIR for keeping the page active? QUESTION: do you know why the results are slightly different from the numbers in the current website readme?  -->

## Parallel computing and tracking progress

Bootstrapping can be computationally intensive. To reduce computation time, we designed this package to work with the [`future`](https://future.futureverse.org/) package for parallel computing [@future].
To enable parallel computation of bootstrap calculations, simply set an appropriate parallelization plan such as

```{r, eval = FALSE}
library(future)
plan(multisession)
```

Our [vignette](https://jepusto.github.io/metaselection/articles/selection-models.html#parallel-processing) includes a more detailed demonstration.

The package is also designed to work with the [`progressr`](https://progressr.futureverse.org/) package [@progressr].
To turn on progress bars for all bootstrap calculations, use

```{r, eval = FALSE}
progressr::handlers(global = TRUE)
```

See [`vignette("progressr-intro")`](https://progressr.futureverse.org/articles/progressr-01-intro.html) for further details.

## Related Work

Several existing meta-analysis packages provide implementations of selection models, but are limited by the assumption of independent effects:

- The `metafor` package [@Viechtbauer2010conducting] includes the `selmodel()` function, which allows users to fit many different types of selection models.
- The `weightr` package [@weightr] includes functions to estimate a class of $p$-value selection models described in @vevea1995general. However, because these packages assume effect sizes to be independent, the results they produce will have incorrect standard errors and misleadingly narrow confidence intervals for datasets containing multiple effects drawn from the same study.
- The `RoBMA` package [@RoBMA] implements Bayesian ensemble models that include step-function selection models as one component of the ensemble. `RoBMA` includes an implementation of a multilevel extension to the step-function selection model, as described in @bartovs2026robust, a different approach for handling dependence that is an alternative to the marginal selection models implemented in `metaselection`.
- The `PublicationBias` package [@PublicationBias] implements sensitivity analyses for selective reporting bias that incorporate cluster-robust variance estimation methods for handling dependent effect sizes. However, the sensitivity analyses implemented in the package are based on a pre-specified degree of selective reporting, rather than allowing the degree of selection to be estimated from the data. The sensitivity analyses are also based on a specific and simple form of selection model, and do not allow consideration of more complex forms of selection functions.

The `metaselection` package goes beyond these other tools both by considering more complex forms of selective reporting and by correcting for selective reporting bias while accommodating meta-analytic datasets that include dependent effect sizes. 

## Acknowledgements

The development of this software was supported, in whole or in part, by the Institute of Education Sciences, U.S. Department of Education, through grant [R305D220026](https://ies.ed.gov/funding/grantsearch/details.asp?ID=5730) to the American Institutes for Research.
The opinions expressed are those of the authors and do not represent the views of the Institute or the U.S.
Department of Education.

## References
