---
title: "Modified Step-Function Selection Model"
output: pdf_document
bibliography: references.bib
editor_options: 
  markdown: 
    wrap: sentence
---

Step-function selection models involve two components. [@hedges2005selection] 
The first component, which we shall call the evidence-generating process, involves assumptions about the distribution of effect size estimates prior to selective reporting.
This component is usually a random effects model or meta-regression model.
The second component, which we shall call the selection process, involves assumptions about how effect size estimates come to be observed and therefore available for inclusion in the meta-analysis. 
Combining the assumptions of both components leads to a model for the distribution of observed effect size estimates, with interpretable parameters describing both the evidence-generating process and the selection process. 

We will use the following notation to describe the model and estimation methods. Consider a meta-analytic sample consisting of $J$ studies, in which study $j$ reports $k_j$ effect size estimates. Let $y_{ij}$ denote observed effect size estimate $i$ from study $j$, defined so that positive values are consistent with theoretical expectations. Each estimate is accompanied by a standard error $\sigma_{ij}$ and corresponding one-sided $p$-value $p_{ij} = 1 - \Phi(y_{ij} /\sigma_{ij})$, where the one-sided $p$-value is defined with respect to the null hypothesis that the effect is less than or equal to zero and the alternative hypothesis that the effect is positive. Let $\mat{x}_{ij}$ be a $1 \times x$ row-vector of predictors that encode characteristics of the effect sizes, samples, or study procedures. Let $\Phi()$ denote the standard normal cumulative distribution function and $\phi()$ denote the standard normal density function.

## Evidence-generating process

We consider an evidence-generating process based on a standard meta-regression model. 
Let $Y^*$ denote an effect size estimate that has been generated from primary study data but might or might not be reported; let $\sigma^*$, $p^*$, and $\mat{x}^*$ denote the corresponding standard error, one-sided $p$-value, and predictor vector.
The evidence-generating process can then be expressed as
\begin{equation}
\label{eq:meta-mean-regression}
\left(Y^* | \sigma^*, \mat{x}^*\right) \sim N\left(\mat{x}^* \bs\beta, \ \tau^2 + \sigma^{*2}\right),
\end{equation}
where $\bs\beta$ is an $x \times 1$ vector of regression coefficients that relate the predictors to average effect size and $\tau^2$ is the variance of the distribution of effect size parameters. 
This random-effects meta-regression treats each observed effect size as if it were independent, even though the data may include multiple, statistically dependent effect size estimates generated from the same sample. 
As a result, the regression coefficients $\boldsymbol\beta$ describe the overall expected effect size (given the predictors) and the variance parameter $\tau^2$ describes the heterogeneity of the marginal effect size distribution, rather than decomposing the heterogeneity into within-study and between-study components. 

## Selection process

At a general level, a $p$-value selection process is defined by a selection function, which specifies the probability that an effect size estimate is reported given its $p$-value. 
Letting $O$ be an indicator for whether the effect size estimate $Y^*$ is observed, the selection process model involves the assumption that $\text{Pr}(O = 1 \ | \ p^*)$ is proportional to a function $w\left(p^*; \bs\lambda \right)$ that maps $p$-values in the interval $[0,1]$ to strictly positive weights based upon an unknown $H \times 1$ parameter vector $\bs\lambda$. 

Vevea and Hedges [@vevea1995general] described a random effects meta-regression model where selection weights vary depending on a set of pre-specified thresholds for the one-sided $p$-value, chosen based on conventional, psychologically salient cut-offs for judging statistical significance.
Let $\alpha_1,...,\alpha_H$ be a set of thresholds for the one-sided p-values, and set $\alpha_0 = 0$, $\alpha_{H+1} = 1$, and $\lambda_0 = 1$. 
A step function selection model is then given by 
\begin{equation}
\label{eq:step-function-p}
w(p^*; \bs\lambda) =  \sum_{h=0}^H \lambda_h \times I\left(\alpha_{h} < p^* \leq \alpha_{h+1}\right), 
\end{equation}
for $\bs\lambda = \left(\lambda_1,...,\lambda_H\right)$. 
Equation (\ref{eq:step-function-p}) can be written equivalently as 
\begin{equation}
\label{eq:step-function-y}
w(Y^*, \sigma^*; \bs\lambda) =  \sum_{h=0}^H \lambda_h \times \left(\sigma^* \Phi^{-1}\left(1 - \alpha_{h+1}\right) \leq Y^*  < \sigma^* \Phi^{-1}\left(1 - \alpha_h\right)\right). 
\end{equation}
Setting $\lambda_0 = 1$ is necessary for identification because the absolute probabilities of selection cannot be estimated. 
The remaining parameters are therefore interpreted as _relative_ probabilities of selection, compared to the probability of selection for an effect size with $p^* \leq \alpha_1$. 

In practice, meta-analysts will often use only a small number of steps in the selection model. 
One common choice is the three-parameter selection model, which has a single step at $\alpha_1 = .025$, as depicted in Figure \@ref(fig:step-functions)a. 
With this choice of threshold, positive effects that are statistically significant at the two-sided level of $p < .05$ have a different probability of selection than effects that are not statistically significant or not in the anticipated direction.
Another possibility is to use two steps at $\alpha_1 = .025$ and $\alpha_2 = .500$, which allows for different probabilities of selection for effects that are positive but not statistically significant and effects that are in the opposite of the expected direction, as depicted in Figure \@ref(fig:step-functions)b.

```{r step-functions}
#| echo: false
#| fig.retina: 2
#| fig.width: 5
#| fig.height: 3.5
#| out.width: 49%
#| fig.cap: "Examples of step functions"
#| fig.subcap:
#|    - "One-step selection with $\\lambda_1 = 0.4$" 
#|    - "Two-step selection with $\\lambda_1 = 0.4, \\lambda_2 = 0.2$"
#| fig.pos: tb 

library(metaselection)
library(ggplot2)
lambda1 <- 0.4
lambda2 <- 0.2
pvals <- seq(0,1,.005)
PSM3 <- step_fun(cut_vals = .025, weights = lambda1)
PSM4 <- step_fun(cut_vals = c(.025, .500), weights = c(lambda1, lambda2))

dat <- data.frame(p = pvals, PSM3 = PSM3(pvals), PSM4 = PSM4(pvals))

PSM3 <- 
  ggplot(dat, aes(x = pvals)) + 
  scale_y_continuous(limits = c(0,1.1), expand = expansion(0,0)) + 
  scale_x_continuous(breaks = seq(0,1,0.2), expand = expansion(0,0)) + 
  geom_vline(xintercept = 0.025, linetype = "dashed") + 
  geom_hline(yintercept = 0) + 
  annotate(geom = "text", x = .06, y = 1.03, label = ".025") + 
  geom_area(aes(y = PSM3), fill = "darkred", alpha = 0.6) +   
  theme_minimal() + 
  labs(x = "p-value (one-sided)", y = "Selection probability")

PSM4 <- 
  ggplot(dat, aes(x = pvals)) + 
  scale_y_continuous(limits = c(0,1.1), expand = expansion(0,0)) + 
  scale_x_continuous(breaks = seq(0,1,0.2), expand = expansion(0,0)) + 
  geom_vline(xintercept = c(0.025, .500), linetype = "dashed") + 
  geom_hline(yintercept = 0) + 
  annotate(geom = "text", x = .06, y = 1.03, label = ".025") + 
  annotate(geom = "text", x = .535, y = 1.03, label = ".500") + 
  geom_area(aes(y = PSM4), fill = "purple", alpha = 0.6) +   
  theme_minimal() + 
  labs(x = "p-value (one-sided)", y = "Selection probability")

PSM3
PSM4
```

## Distribution of observed effect size estimates

Combining the assumptions of the evidence-generating process and the selection process leads to a model for an observed effect size estimate. 
The marginal distribution of an observed effect size estimate $Y$ with standard error $\sigma$ is equivalent to the distribution of $Y^*$ given that $O = 1$, with density function
\begin{equation}
\label{eq:generic-selection}
f(Y = y | \sigma, \mat{x}) = \frac{w\left(y, \sigma; \bs\lambda \right)}{A(\mat{x}, \sigma; \bs\beta, \tau^2, \bs\lambda)} \times \frac{1}{\sqrt{\tau^2 + \sigma^2}} \phi\left(\frac{y - \mat{x} \bs\beta}{\sqrt{\tau^2 + \sigma^2}}\right),
\end{equation}
where 
\begin{equation}
\label{eq:generic-selection-A}
A(\mat{x}, \sigma; \bs\beta, \tau^2, \bs\lambda) =  \int_\mathbb{R} w\left(y, \sigma; \bs\lambda \right) \times  \frac{1}{\sqrt{\tau^2 + \sigma^2}}\phi\left(\frac{y - \mat{x}\bs\beta}{\sqrt{\tau^2 + \sigma^2}}\right) dy.
\end{equation}
If $w(y, \sigma; \bs\lambda) = 1$ for all possible $y$, then there is no selective reporting, $A(\mat{x}, \sigma; \bs\beta, \tau^2, \bs\lambda) = 1$, and the density reduces to the unweighted density of a random-effects meta-regression model.
The $A(\mat{x}, \sigma; \bs\beta, \tau^2, \bs\lambda)$ term can be computed using the closed-form expression
\begin{equation}
\label{eq:step-function-A}
A(\mat{x}, \sigma; \bs\beta, \tau^2, \bs\lambda) = \sum_{h=0}^H \lambda_h B_{h}
\end{equation}
where 
$B_{h} = \Phi\left(c_{h}\right) - \Phi\left(c_{h+1}\right)$ and $c_{h} = \left[\sigma \Phi^{-1}\left(1 - \alpha_h\right) - \mat{x}\bs\beta\right] / \sqrt{\tau^2 + \sigma^2}$ for $h = 0,...,H$. [@vevea1995general]


## Estimation Methods {#estimation-methods}

Past developments of selection models have focused on maximum likelihood estimation [@hedges1992modeling; @vevea1995general; @citkowicz2017parsimonious] or Bayesian estimation  under the assumption that all effect sizes are mutually independent [@Guan2016bayesian; @Larose1998modeling; @Maier2023robust] or on sensitivity analysis methods that treat the selection model as known [@vevea2005publication; @mathur2020sensitivity]. We consider two estimation and inference strategies that build upon and generalize past approaches, including maximum penalized marginal likelihood and an alternative based on re-weighting the Gaussian likelihood of the evidence-generating process.
For purposes of estimation, we write the likelihoods using natural log transformations of the variance parameter and selection parameters, with $\gamma = \log \tau^2$, $\zeta_h = \log \lambda_h$, and $\bs\zeta = \left[\zeta_1,...,\zeta_H\right]'$. 

With both estimation approaches, we incorporate prior penalty terms on all model parameters, which regularize the likelihood and markedly improve the convergence properties of the estimation algorithms.[@VanHouwelingen2001shrinkage; @Cole2014maximum]
The penalty terms are equivalent to putting independent priors on each element of the parameters.[@Chung2013nondegenerate]
Let $p_{\bs\beta}(\bs\beta)$, $p_{\gamma}(\gamma)$, and $p_{\bs\zeta}(\bs\zeta)$ denote the log-prior penalties on the corresponding parameters. 
We describe the specific form of the penalty terms after outlining the estimation methods.

With both estimation approaches, we also allow for incorporation of weights, which permits efficient calculation for a variety of bootstrapping techniques.
Thus, let $a_{11},...,a_{J k_j}$ be an arbitrary set of weights assigned to each effect size estimate; in a typical, unweighted analysis, all weights will be equal to $a_{ij} = 1$.

### Maximum penalized marginal likelihood

Composite marginal likelihood techniques involve working with the marginal distribution of each observed effect size estimate as if they were all mutually independent. [@cox2004note; @lindsay1988composite; @varin2008composite]
Thus, we assume that the observed effect size estimates were generated from Equation \@ref(eq:generic-selection). 
The log of the marginal likelihood contribution for effect size estimate $i$ from study $j$ is given by
\begin{align}
l^M_{ij}\left(\bs\beta, \gamma, \bs\zeta \right) &= \log f\left(Y = y_{ij} | \sigma_{ij}, \mat{x}_{ij}\right) \nonumber \\
&= \log w\left(y_{ij}, \sigma_{ij}; \bs\zeta \right) - \log A\left(\mat{x}_{ij}, \sigma_{ij}; \bs\beta, \gamma, \bs\zeta \right) \nonumber\\
& \qquad \qquad   - \frac{1}{2} \frac{\left(y_{ij} - \mat{x}_{ij} \bs\beta\right)^2}{\exp(\gamma) + \sigma_{ij}^2} - \frac{1}{2}\log\left(\exp(\gamma) + \sigma_{ij}^2\right) - \frac{1}{2}\log(2 \pi). \label{eq:log-like-ij}
\end{align}
The weighted, penalized marginal log-likelihood across all $J$ studies is then
\begin{equation}
\label{eq:marginal-likelihood}
l^M\left(\bs\beta, \gamma, \bs\zeta\right) = \sum_{j=1}^J \sum_{i=1}^{k_j} a_{ij} l^M_{ij}\left(\bs\beta, \gamma, \bs\zeta\right) + p_{\bs\beta}(\bs\beta) + p_{\gamma}(\gamma) + p_{\bs\zeta}(\bs\zeta).
\end{equation}
The penalized marginal likelihood (PML) estimators, denoted as $\bs{\hat\beta}$, $\hat\gamma$, and $\bs{\hat\zeta}$, are obtained as the set of parameter values that maximize the penalized marginal log-likelihood for the observed data, as given in Equation (\ref{eq:marginal-likelihood}).

If the true parameter values are not at the extremes of their ranges, the CML estimator can also be defined as the solution of the weighted score equations, 
\begin{equation}
\label{eq:marginal-score-equations}
\sum_{j=1}^J \mat{S}_{j}\left(\bs{\hat\beta}, \hat\gamma, \bs{\hat\zeta}\right) + p'\left(\bs{\hat\beta}, \hat\gamma, \bs{\hat\zeta}\right) = \mat{0}
\end{equation}
where $\mat{S}_{j}\left(\bs{\beta}, \gamma, \bs{\zeta}\right)$ denotes the score vector for study $j$, consisting of derivatives of the likelihood contributions for study $j$ with respect to the component parameters, and $p'(\bs\beta, \gamma, \bs\zeta)$ denotes the vector of derivatives of the prior penalty terms with respect to the component parameters.
`r appendix_prefix` \@ref(PML-derivatives) provides exact expressions for the score vectors and derivatives of the prior penalties.

Robust variance estimators, or sandwich estimators, are a commonly used technique for quantifying the uncertainty in CML estimators. Let $\mat{H}$ denote the Hessian matrix of the composite log-likelihood,
\begin{equation}
\mat{H}(\bs\beta, \gamma, \bs\zeta) = \sum_{j=1}^J \frac{\partial \mat{S}_j(\bs\beta, \gamma, \bs\zeta)}{\partial \left(\bs\beta' \ \gamma \ \bs\zeta'\right)},
\end{equation}
exact expressions for which are given in `r appendix_prefix` \@ref(PML-derivatives).
Let $\mat{\hat{S}}_j = \mat{S}_j(\bs{\hat\beta}, \hat\gamma, \bs{\hat\zeta})$ and $\mat{\hat{H}} = \mat{H}(\bs{\hat\beta}, \hat\gamma, \bs{\hat\zeta})$ denote the score vectors and Hessian matrix evaluated at the maximum of the composite likelihood.
A cluster-robust sandwich estimator of the sampling variance of the CML estimator is then
\begin{equation}
\label{eq:sandwich-variance}
\mat{V}^{CML} = \mat{\hat{H}}^{-1}\left(\sum_{j=1}^J \mat{\hat{S}}_j {\mat{\hat{S}}_j}'\right) \mat{\hat{H}}^{-1}.
\end{equation}
We construct confidence intervals for model parameters using $\mat{V}^{CML}$ with Wald-type large sample approximations. For instance, the $(1 - 2\alpha)$-level large-sample confidence interval for a meta-regression parameter $\beta_g$ is constructed as
$$
\hat\beta_g \ \pm \ \Phi^{-1}(1 - \alpha) \times \sqrt{V^{CML}_{gg}},
$$
where $V^{CML}_{gg}$ is the $g^{th}$ diagonal entry of $\mat{V}^{CML}$.


### Augmented, re-weighted Gaussian likelihood

Penalized marginal likelihood is not the only possible basis for deriving estimators of selection model parameters. 
In the framework of a sensitivity analysis for worst-case selection bias, Mathur and VanderWeele @mathur2020sensitivity proposed using regular meta-analytic estimators for $\bs\beta$, but with weights defined by the inverse probability of selection under a step-function selection model with a single step at $\alpha_1 = .025$.
Because they were working in the context of sensitivity analysis, they assumed a maximum plausible degree of selection rather than estimating the parameters of a selection model, so that the weights were fixed and known quantities. 
In contrast, here we will consider a more general model, possibly with multiple steps, using weights derived by estimating the selection model parameters.
We describe the estimators as augmented, re-weighted Gaussian likelihood (ARGL) estimators because the Gaussian likelihood of the evidence-generating process is re-weighted based on the selection process, with selection process parameters identified by augmenting the likelihood with an additional estimating equation.
We study this additional estimation method because it is computationally less demanding than the PML estimator and because it is based on a different estimation framework. It might therefore have better convergence rates or different robustness properties than the PML estimator.

Given the parameters of the selection process, we can calculate relative probabilities of selection for each effect size estimate, $w_{ij} = w(y_{ij}, \sigma_{ij}; \bs\zeta)$. We use these selection probabilities to form weighted estimating equations for the evidence-generating process. Under the evidence-generation model, the marginal log-likelihood of effect size estimate $i$ from study $j$ is Gaussian, given by
$$
l^G_{ij}(\bs\beta, \gamma) = - \frac{1}{2}\frac{(y_{ij} - \mat{x}_{ij} \bs\beta)^2}{\exp(\gamma) + \sigma_{ij}^2} - \frac{1}{2}\log(\exp(\gamma) + \sigma_{ij}^2) - \frac{1}{2} \log(2\pi).
$$
Allowing for weights, the re-weighted Gaussian log-likelihood contribution of study $j$ is
$$
l_j^G(\bs\beta, \gamma, \bs\zeta) = \sum_{i=1}^{k_j} \frac{a_{ij}} {w_{ij}} \times l^G_{ij}(\bs\beta, \gamma)
$$
and the penalized likelihood of all $J$ studies is given by
\begin{equation}
\label{eq:Gaussian-log-lik}
l^G(\bs\beta, \gamma, \bs\zeta) = \sum_{j=1}^J \sum_{i=1}^{k_j} \frac{a_{ij}} {w_{ij}} \times l^G_{ij}(\bs\beta, \gamma) + p_{\bs\beta}(\bs\beta) + p_{\gamma}(\gamma).
\end{equation}
If the parameters of the selection process were known, we could find estimators for $\bs\beta$ and $\gamma$ by maximizing $l^G(\bs\beta, \gamma, \bs\zeta)$ for a fixed value of $\bs\zeta$.
To estimate the full set of model parameters, we augment the Gaussian likelihood by borrowing the estimating equation for $\bs\zeta$ from the maximum penalized marginal likelihood approach.

The ARGL estimator can be defined more precisely by a set of estimating equations.
Let $\mat{S}^G_{\bs\beta j} (\bs\beta, \gamma, \bs\zeta)$ and $\mat{S}^G_{\gamma j} (\bs\beta, \gamma, \bs\zeta)$ denote the derivatives of $l_j^G(\bs\beta, \gamma, \bs\zeta)$ with respect to $\bs\beta$ and $\gamma$, respectively, the exact form of which is given in `r appendix_prefix` \@ref(ARGL-derivatives).
Let $\mathbf{S}_{\bs\zeta j}\left(\bs{\beta}, \gamma, \bs{\zeta}\right)$ denote the derivative with respect to $\bs\zeta$ of the contribution of study $j$ in Equation \@ref(eq:marginal-likelihood) . 
Stacking these derivatives as
\begin{equation}
\label{eq:hybrid-score}
\mat{M}_j(\bs\beta, \gamma, \bs\zeta) = \left[\begin{array}{c} \mat{S}^G_{\bs\beta j}(\bs\beta, \gamma, \bs\zeta) \\ S^G_{\gamma j}(\bs\beta, \gamma, \bs\zeta) \\ \mat{S}_{\bs\zeta j}(\bs\beta, \gamma, \bs\zeta) \end{array}\right],
\end{equation}
we define the ARGL parameter estimators $\bs{\tilde\beta}$, $\tilde\gamma$, and $\bs{\tilde\zeta}$ as the solution to the penalized estimating equations 
\begin{equation}
\label{eq:hybrid-total-score}
\sum_{j=1}^J \mat{M}_j(\bs{\tilde\beta}, \tilde\gamma, \bs{\tilde\zeta}) + p'\left(\bs{\tilde\beta}, \tilde\gamma, \bs{\tilde\zeta}\right) = \mat{0},
\end{equation}
with $p'\left(\bs{\beta}, \gamma, \bs{\zeta}\right)$ as defined in Equation \@ref(eq:marginal-score-equations).

We consider conducting inferences for the ARGL estimators using cluster-robust sandwich variance estimators that have the same form as (\ref{eq:sandwich-variance}). 
`r appendix_prefix` \@ref(ARGL-derivatives) provides further details.
We construct confidence intervals for model parameters using Wald-type large sample approximations, just as with the CML estimators.

### Prior penalties

For both estimation methods, we specify weak prior penalties selected to regularize outlying values without substantially shifting the estimator in most datasets.
To this end, we use $\mathcal{L}_4$-norm prior penalties for the mean parameters $\bs\beta$, given by
\begin{equation}
\label{eq:beta-prior}
p_{\bs\beta}(\bs\beta) = -\frac{1}{16} \sum_{p=1}^x \beta_p^4.
\end{equation}
This prior penalty is depicted in Figure \@ref(fig:prior-penalties)a. The penalty is nearly flat when $|\beta_p| < 1$, but becomes sharper and more informative when $|\beta_p| > 2$.
It is strictly weaker than the penalty corresponding to a $N(0,1)$ prior when $|\beta_p| < 2.8$. 
For the log of the heterogeneity parameter, we use 
\begin{equation}
\label{eq:gamma-prior}
p_{\gamma}(\gamma) = \frac{1}{2} \gamma - 5 \exp\left(\frac{\gamma}{2}\right),
\end{equation}
as depicted in Figure \@ref(fig:prior-penalties)b.
This penalty corresponds to putting a $\Gamma(1, \frac{1}{5})$ prior on $\tau$, as used in past work on priors for variance parameters in multilevel models. [@Chung2013nondegenerate]
The penalty term reaches a maximum at $\gamma = \log(0.2)$ and remains weak for smaller degrees of heterogeneity; because it is asymmetric, it more heavily penalizes large values of $\gamma$.
For the log-scale selection parameters $\bs\zeta$, we use $\mathcal{L}_4$-norm prior penalties, given by
\begin{equation}
\label{eq:zeta-prior}
p_{\bs\zeta}(\bs\zeta) = -\frac{1}{54} \sum_{h=1}^H \left(\zeta_h - \log\left(\frac{1}{2}\right)\right)^4
\end{equation}
and depicted in Figure \@ref(fig:prior-penalties)c.
This penalty is centered at a selection weight of $\lambda = \frac{1}{2}$ so that it remains very weak over the range of $\lambda = \frac{1}{20}$ (strong selective reporting) to $\lambda = 1$ (no selective reporting), consistent with the range of selective reporting observed in an empirical review of meta-analyses in psychology and clinical medicine.[@mathur2021estimating]
It more heavily penalizes extremely strong selection levels $(\lambda < \frac{1}{50})$ and selective reporting that strongly _favors_ non-significant findings $(\lambda > 8)$.


```{r prior-penalties}
#| echo: false
#| fig.retina: 2
#| fig.width: 5
#| fig.height: 3
#| fig.ncol: 2
#| out.width: 49%
#| fig.cap: "Prior penalty functions for step function model parameters"
#| fig.subcap:
#|    - "Prior penalty for mean parameter $\\bs\\beta$. Dashed line corresponds to a standard normal penalty." 
#|    - "Prior penalty for heterogeneity parameter $\\gamma$" 
#|    - "Prior penalty for selection parameter $\\bs\\zeta$" 
#| fig.pos: tb 

tibble(
  beta = seq(-3,3, length.out = 200)
) %>%
  mutate(
    p_beta = -beta^4 / 16,
    z = -beta^2 / 2
  ) %>%
ggplot() + 
  aes(beta) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) + 
  geom_line(aes(y = p_beta), color = "darkgreen", alpha = 0.6, linewidth = 1) +   
  geom_line(aes(y = z), linetype = "dashed", alpha = 0.6) +   
  scale_x_continuous(breaks = -3:3, expand = expansion(0,0)) + 
  scale_y_continuous(expand = expansion(0,0)) + 
  coord_cartesian(ylim = c(-4,0)) + 
  theme_minimal() + 
  labs(x = expression(beta[p]), y = expression(p[beta](beta[p])))

tau_bench <- c(0.01, 0.05, 0.1, 0.2, 0.4, 0.6, 1)

tibble(
  gamma = seq(log(0.01^2), log(1), length.out = 200),
) %>%
  mutate(
    tau = exp(gamma / 2),
    p_gamma = 0.5 * gamma - 5 * exp(gamma / 2),
    p_gamma = p_gamma - max(p_gamma)
  ) %>%
ggplot() + 
  aes(tau) + 
  geom_hline(yintercept = 0) + 
  geom_line(aes(y = p_gamma), color = "darkgreen", alpha = 0.6, linewidth = 1) +   
  theme_minimal() + 
  scale_x_continuous(
    transform = "log", 
    breaks = tau_bench,
    expand = expansion(0,0)
  ) + 
  scale_y_continuous(expand = expansion(0,0)) + 
  coord_cartesian(ylim = c(-4,0)) + 
  labs(x = expression(tau == exp(gamma / 2)), y = expression(p[gamma](gamma)))


lambda_bench <- c(0.02, 0.05, 0.10, 0.20, 0.50, 1, 2, 4, 8)

tibble(
  zeta = seq(log(0.01), log(8), length.out = 500)
) %>%
  mutate(
    lambda = exp(zeta),
    p_zeta = -(zeta - log(0.5))^4 / 54,
  ) %>%
ggplot() + 
  aes(lambda) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 1) + 
  geom_line(aes(y = p_zeta), color = "darkgreen", alpha = 0.6, linewidth = 1) +   
  theme_minimal() + 
  scale_x_continuous(
    transform = "log", 
    breaks = lambda_bench,
    expand = expansion(0,0)
  ) + 
  scale_y_continuous(expand = expansion(0,0)) + 
  coord_cartesian(ylim = c(-4,0)) + 
  labs(x = expression(tau == exp(zeta[q])), y = expression(p[zeta](zeta[q])))
```


## Bootstrap inference

Sandwich estimators such as those in Equations \@ref(eq:sandwich-variance) require a large number of independent clusters (i.e., large $J$) to provide accurate assessments of uncertainty. 
We consider alternative inference techniques based on bootstrapping, which might provide more accurate inference with a limited number of clusters.
Bootstrap techniques involve generating many new pseudo-samples of observations by randomly perturbing the original sample, then re-calculating an estimator using each pseudo-sample.
The distribution of the estimator across pseudo-samples is used as a proxy for the actual sampling distribution of the estimator, providing a basis for calculating standard errors and confidence intervals.[@boos2003introduction]

Many different bootstrap sampling schemes have been described that apply to different data structures and require different assumptions.[@davison1997bootstrap]
In order to fully capture the uncertainty of the parameter estimates, it is crucial that the process used to generate pseudo-samples accounts for the dependence structure of the observations.
Techniques that do so include the non-parametric clustered bootstrap, two-stage bootstrap,[@field2007bootstrapping; @leeuw2008resampling] and fractional random weight bootstrap.[@xu2020applications] 
Here, we focus on the two-stage bootstrap; details about other bootstrap techniques can be found in `r appendix_prefix` \@ref(bootstrap-resampling).

In the two-stage bootstrap, each pseudo-sample is generated by randomly drawing $J$ clusters of observations with replacement from the original sample and then randomly re-sampling observations with replacement from each selected cluster. 
This process amounts to simulating a set of weights. Let $a_j^{(b)}$ be a first-stage weight for cluster $j$ and $a_{ij}^{(b)}$ be the weight assigned to observation $i$ in cluster $j$ for pseudo-sample $b$.
The two-stage bootstrap is equivalent to first drawing $a_1^{(b)},...,a_J^{(b)}$ from a multinomial distribution with $J$ trials and equal probability on each of $J$ categories, then drawing $a_{1j}^{(b)},...,a_{k_j j}^{(b)}$ from a multinomial distribution with $a_j^{(b)} \times k_j$ trials and equal probability on each of $k_j$ categories, for $j = 1,...,J$.

For constructing confidence intervals, bootstrapping entails generating a total of $B$ pseudo-samples, where $B$ is a large number such as 1999, and re-calculating the estimator for each pseudo-sample. 
There are several methods for constructing confidence intervals from a bootstrap distribution.
We consider four standard methods [@davison1997bootstrap], including the percentile CI, basic CI, studentized CI, and the bias-corrected-and-accelerated CI proposed by Efron.[@efron1987better]
`r appendix_prefix` \@ref(bootstrap-CI-construction) provides further details about the bootstrap CI calculations.
