---
title: "Additional simulation results"
output: pdf_document
bibliography: references.bib
editor_options: 
  markdown: 
    wrap: sentence
---
```{r}
source("process-simulation-results.R")

mu_graph_res_main$method = fct(mu_graph_res_main$method, levels = c("Beta","CHE-ISCW","PET/PEESE"))
mu_graph_res_ci_main$method = fct(mu_graph_res_ci_main$method, levels = c("Beta","CHE-ISCW","PET/PEESE"))

mu_graph_res_miss$method = fct(mu_graph_res_miss$method, levels = c("Beta","3PSM","4PSM"))
mu_graph_res_ci_miss$method = fct(mu_graph_res_ci_miss$method, levels = c("Beta","3PSM","4PSM"))

```

# Beta-Function Selection Model Compared to CHE-ISCW and PET/PEESE
<!-- Need a better header name -->

## Additional simulation results for methods of estimating the average effect size $(\mu)$ {#mu-simulation-results-main}

```{r convergence-rates-main}
#| cache: true
#| fig.width: 9
#| fig.height: 6.5
#| fig.env: "sidewaysfigure"
#| fig.cap: "Convergence rates of the beta-function selection model by selection probability, average SMD, and between-study heterogeneity. Points correspond to median convergence rates; thin lines correspond to range of convergence rates; thick lines correspond to inter-decile range."

mu_graph_res_main %>%
  filter(model_estimator %in% c("beta_CML")) %>%
  group_by(mean_smd, tau, selection_strength, method) %>%
  summarize(
    min = min(convergence),
    Q10 = quantile(convergence, 0.1),
    median = median(convergence),
    Q90 = quantile(convergence, 0.9),
    max = max(convergence),
    .groups = "drop"
  ) %>%
ggplot() + 
  aes(x = selection_strength, y = median, ymin = min, max = max, color = method, fill = method) +
  geom_pointrange(
    position = position_dodge(width = 0.5)
  ) + 
  geom_linerange(
    aes(ymin = Q10, ymax = Q90),
    position = position_dodge(width = 0.5),
    linewidth = 1.2
  ) + 
  scale_color_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 3)) +
  expand_limits(y = 0.99) + 
  facet_grid(
    tau ~ mean_smd, 
    labeller = label_bquote(
      rows = tau == .(tau),
      cols = mu == .(mean_smd)
    ),
    scales = "free_y"
  ) +
  labs(
    x = "Selection probability", 
    y = "Convergence rate", 
    color = "Method",
    fill = "Method"
  ) + 
  theme_bw() +
  theme(legend.position = "top")

```

```{r rmse-CHE-Beta-main}
#| cache: true
#| fig.width: 9
#| fig.height: 6.5
#| fig.env: "sidewaysfigure"
#| fig.cap: "Ratio of root mean-squared error for CHE-ISCW estimator to root mean-squared error of CML estimator by selection probability, number of studies, average SMD, and between-study heterogeneity"

RMSE_comparison_plot(mu_wide_res_main, "Beta","CHE-ISCW")
```

```{r rmse-PET-Beta-main}
#| cache: true
#| fig.width: 9
#| fig.height: 6.5
#| fig.env: "sidewaysfigure"
#| fig.cap: "Ratio of root mean-squared error for PET/PEESE estimator to root mean-squared error of CML estimator by selection probability, number of studies, average SMD, and between-study heterogeneity"

RMSE_comparison_plot(mu_wide_res_main, "Beta","PET/PEESE")
```

```{r comparison-coverage-full-main}
#| cache: true
#| fig.width: 9
#| fig.height: 6.5
#| fig.env: "sidewaysfigure"
#| fig.cap: "Coverage levels of confidence intervals for the average effect size based on cluster-robust variance approximations, by method, number of studies, average SMD, and between-study heterogeneity. Dashed lines correspond to the nominal confidence level of 0.95."

mu_graph_res_ci_main %>%
  filter(
    CI_type %in% c("large-sample")
  ) %>%
  ggplot(aes(x = J, y = coverage, color = method, fill = method)) +
  geom_boxplot(alpha = .5, coef = Inf) +
  geom_hline(yintercept = 0.95, linetype = "dashed") +
  scale_y_continuous(limits = c(NA, 1), expand = expansion(0,0)) + 
  scale_color_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  facet_grid(
    tau ~ mean_smd, 
    labeller = label_bquote(
      rows = tau == .(tau),
      cols = mu == .(mean_smd)
    ),
    scales = "free_y"
  ) +
  labs(
    x = "Number of studies (J)", 
    y = "Coverage rate", 
    color = "Method",
    fill = "Method"
  ) + 
  theme_bw() +
  theme(legend.position = "top")

```

# Beta-Function Selection Model Compared to 3PSM and 4PSM Step-Function Selection Models
<!-- Need a better header name -->

## Additional simulation results for methods of estimating the average effect size $(\mu)$ {#mu-simulation-results-miss}

```{r comparison-coverage-full-miss}
#| cache: true
#| fig.width: 9
#| fig.height: 6.5
#| fig.env: "sidewaysfigure"
#| fig.cap: "Coverage levels of confidence intervals for the average effect size based on cluster-robust variance approximations, by method, number of studies, average SMD, and between-study heterogeneity. Dashed lines correspond to the nominal confidence level of 0.95."

mu_graph_res_ci_miss %>%
  filter(
    CI_type %in% c("large-sample")
  ) %>%
  ggplot(aes(x = J, y = coverage, color = method, fill = method)) +
  geom_boxplot(alpha = .5, coef = Inf) +
  geom_hline(yintercept = 0.95, linetype = "dashed") +
  scale_y_continuous(limits = c(NA, 1), expand = expansion(0,0)) + 
  scale_color_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  facet_grid(
    tau ~ mean_smd, 
    labeller = label_bquote(
      rows = tau == .(tau),
      cols = mu == .(mean_smd)
    ),
    scales = "free_y"
  ) +
  labs(
    x = "Number of studies (J)", 
    y = "Coverage rate", 
    color = "Method",
    fill = "Method"
  ) + 
  theme_bw() +
  theme(legend.position = "top")

```
