---
title             : "Estimating beta-function selection models in meta-analysis with dependent effects"
shorttitle        : "beta-function selection models"

author: 
  - name          : "Martyna Citkowicz"
    corresponding : yes    # Define only one corresponding author
    affiliation   : "1"
    address       : "Address"
    email         : "mcitkowicz@air.org"
  - name          : "James E. Pustejovsky"
    affiliation   : "2"
    address       : "1082C Educational Sciences, 1025 W Johnson St. Madison, WI 53706-1706"
    email         : "pustejovsky@wisc.edu"
affiliation:
  - id            : "1"
    institution   : "American Institutes for Research"
  - id            : "2"
    institution   : "University of Wisconsin-Madison"

note              : "\\ \\newline `r format(Sys.Date(), '%B %d, %Y')`"

abstract: |
  
  
keywords          : "meta-analysis; dependent effect sizes; selection models; selective reporting; publication bias"

bibliography      : references.bib

figsintext        : yes
figurelist        : no
floatsintext      : yes 
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no
numbersections    : yes
keep_tex          : yes
lang              : "en-US"
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
output            : 
  papaja::apa6_pdf
replace_ampersands: yes

header-includes:
- \usepackage{booktabs}
- \usepackage{multirow}
- \usepackage{multicol}
- \usepackage{amsthm}
- \newtheorem{thm}{Theorem}
- \newtheorem{lem}{Lemma} 
- \usepackage{amsfonts}
- \usepackage{caption}
- \usepackage{multirow}
- \usepackage{float}
- \usepackage{subfig}
- \usepackage{longtable}
- \usepackage[figuresright]{rotating}
- \geometry{twoside=false, top=1in, bottom=1in, left=1in, right=1in}
- \usepackage{hyperref}
- \hypersetup{hidelinks}
- \raggedbottom
- \usepackage{setspace}
- \AtBeginEnvironment{tabular}{\singlespacing}
- \newcommand{\Prob}{\text{Pr}}
- \newcommand{\E}{\text{E}}
- \newcommand{\Cov}{\text{Cov}}
- \newcommand{\cor}{\text{cor}}
- \newcommand{\Var}{\text{Var}}
- \newcommand{\diag}{\text{diag}}
- \newcommand{\mat}[1]{\mathbf{#1}}
- \newcommand{\bs}{\boldsymbol}
- \newcommand{\trace}{\text{tr}}

---

```{r setup, include = FALSE}
library(knitr)
library(papaja)
library(metaselection)
library(tidyverse)
library(CRediTas)

options(tinytex.verbose = TRUE)

opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(tinytex.clean = FALSE, knitr.kable.NA = '')

appendix_prefix <- "Appendix"
```

# Highlights {-}

## What is already known {-}

## What is new {-}

## Potential impact for RSM readers {-}

\newpage

# Estimating beta-function selection models in meta-analysis with dependent effects {#introduction}

```{r child = "introduction.Rmd"}
```

# Models and Estimation Methods {#model-and-estimation}

```{r child = "model-and-estimation-methods.Rmd"}
```

# Empirical Example {#empirical-example}

```{r child = "empirical-example.Rmd"}
```

# Simulation Methods {#simulation-methods}

```{r child = "simulation-methods.Rmd"}
```

# Simulation Results {#simulation-results}

```{r child = "simulation-results.Rmd"}
```

# Discussion {#discussion}

# Author Contributions {-}

```{r CRediT}
#| results: asis

MC_credit <- 
  template_create(authors = "MC") %>%
  mutate(
    Conceptualization = 1,
    Methodology = 1,
    `Formal Analysis` = 1,
    Investigation = 1,
    `Writing - original draft` = 1,
    `Writing - review & editing` = 1,
    `Project administration` = 1,
    `Funding acquisition` = 1
  )

JEP_credit <- 
  template_create(authors = "JEP") %>%
  mutate(
    Conceptualization = 1,
    Methodology = 1,
    Software = 1,
    Validation = 1,
    `Formal Analysis` = 1,
    Investigation = 1,
    Resources = 1,
    `Writing - original draft` = 1,
    `Writing - review & editing` = 1,
  )

bind_rows(MC_credit, JEP_credit) %>%
  cras_write() %>%
  cat()
```

# Funding {-}

This work was supported, in part, by the Institute of Educational Sciences, U.S. Department of Education through grant R305D220026 to the American Institutes of Research.
The opinions expressed are those of the authors and do not represent the views of the Institute of the U.S. Department of Education.

# Acknowledgements {-}

# Data and Replication Materials {-}

Code and data for replicating the empirical example and the Monte Carlo simulation study are available on the Open Science Framework at <url>.

<!-- Add URL for replication package. -->

# Conflict of Interest Statement {-}

The authors declare no conflicts of interest.

# References {-}

\begingroup
<div id="refs" custom-style="Bibliography"></div>
\endgroup

# (APPENDIX) Appendix {-}

```{r child = "appendix-simulation-results.Rmd"}
```
