---
title: "Empirical Application"
output: pdf_document
bibliography: references.bib
---

```{r, echo = F, warning = F, message = F}
library(metaselection)
library(metadat)
library(metafor)
library(tidyverse)
library(here)
#devtools::load_all()

sci <- read_csv(here('tests/testdata','ScienceMeta.csv'))

sci <- sci |>
  rename(esid = es_id, studyid = study_id) |>
  mutate(
    d = yi,
    Va = vi,
    Var_d = Va,
    sd_d = sqrt(Var_d),
    var_d = Var_d,
    p_onesided = 1 - pnorm(d / sd_d)
  )

num_studies <- length(unique(sci$studyid))
num_effects <- length(unique(sci$esid))
```

To demonstrate the interpretation of the beta-function selection model in practice, we reanalyzed the data from a meta-analysis of the effects of science interventions on K–12 student science achievement, conducted by BSCS Science Learning [@taylor2018science]. The meta-analytic sample included findings from `r num_studies` studies with `r num_effects` effects. Approximately half of the studies contributed multiple effects per study, due to either multiple samples or multiple outcomes, leading to dependent effect sizes. Effect sizes were measured as standardized mean differences representing the effects of the interventions on student achievement outcomes, with positive effects corresponding to improvements in student achievement. 

```{r science-learning-models}
#| echo: false
#| warning: false
#| message: false
#| cache: true

# Unadjusted model
sci_unadj_mean <- rma.uni(
  data = sci,
  yi = d,
  sei = sd_d,
  method = "ML"
) |> 
  robust(cluster = studyid, clubSandwich = TRUE)

# Beta model
sci_adj_beta_mean <- selection_model(
  dat = sci,
  yi = d,
  sei = sd_d,
  pi = p_onesided,
  cluster = studyid,
  selection_type = "beta",
  steps = c(.025,.975)
)


# Single-step model
sci_adj_step3_mean <- selection_model(
  dat = sci, 
  yi = d,
  sei = sd_d,
  cluster = studyid,
  selection_type = "step",
  steps = 0.025
)

# Two-step model
sci_adj_step4_mean <- selection_model(
  dat = sci, 
  yi = d,
  sei = sd_d,
  cluster = studyid,
  selection_type = "step",
  steps = c(0.025, .5)
)


# Unadjusted model - moderator

sci_unadj_mod <- rma.uni(
  data = sci,
  yi = d,
  sei = sd_d,
  method = "ML",
  mods = ~ outcome_type_author
) |>
  robust(cluster = studyid, clubSandwich = TRUE)

# Beta model - moderator
sci_adj_beta_mod <- selection_model(
  dat = sci,
  yi = d,
  sei = sd_d,
  pi = p_onesided,
  cluster = studyid,
  mean_mods = ~ outcome_type_author,
  selection_type = "beta",
  steps = c(.025,.975)
  
)

# Single-step model - moderator
sci_adj_step3_mod <- selection_model(
  dat = sci, 
  yi = d,
  sei = sd_d,
  cluster = studyid,
  mean_mods = ~ outcome_type_author,
  selection_type = "step",
  steps = 0.025
)

# Two-step model - moderator
sci_adj_step4_mod <- selection_model(
  dat = sci, 
  yi = d,
  sei = sd_d,
  cluster = studyid,
  mean_mods = ~ outcome_type_author,
  selection_type = "step",
  steps = c(0.025, .5)
)

```

We conducted the analyses using R Version 4.4.3 [@rcoreteam].
We first used the `rma.uni()` function from the `metafor` package to fit a standard random-effects model based on an independent effects working model with random effects for each effect size [@Viechtbauer2010conducting], with standard errors clustered by study. 
The overall estimate of the average effect using the unadjusted model was `r formatC(sci_unadj_mean$beta, format = "f", digits = 2)`, cluster-robust 95% CI [`r formatC(sci_unadj_mean$ci.lb, format = "f", digits = 2)`, `r formatC(sci_unadj_mean$ci.ub, format = "f", digits = 2)`], significantly different from zero $(p `r format.pval(sci_unadj_mean$pval, digits = 3, eps = 1e-3)`)$. 
The unadjusted estimate of heterogeneity was $\tau = `r formatC(sqrt(sci_unadj_mean$tau2), format = "f", digits = 2)`$.

To adjust for selective reporting, we used the `selection_model()` function from the `metaselection` package [@metaselection] to fit the beta-density selection model (with default truncation thresholds of $\alpha_1 = .025, \alpha_2 = .975$) and two different step-function selection models---a single-step model ($\alpha_1 = 0.025$) and a two-step model ($\alpha_1 = .025, \alpha_2 = .5$). Consistent with the methods described above, all three selection models were estimated using the PML approach and an independent-effects working model, with cluster-robust variance estimation used to account for dependent effect sizes.
<!-- JEP: Should we report bootstrap CIs instead? -->
<!-- JEP: Also, the beta function model does not fit as well as either of the step function models (the two-step model is best). -->

```{r science-learning-res, tab.pos = "tb", tab.cap="science learning meta-analysis"}

all_res_mean <- 
  bind_rows(
    beta = sci_adj_beta_mean$est,
    `one-step` = sci_adj_step3_mean$est,
    `two-step` = sci_adj_step4_mean$est,
    .id = "Model"
  ) %>%
  rownames_to_column() 

all_res_mod <- 
  bind_rows(
    beta = sci_adj_beta_mod$est,
    `one-step` = sci_adj_step3_mod$est,
    `two-step` = sci_adj_step4_mod$est,
    .id = "Model"
  ) %>%
  rownames_to_column()

all_res <- 
  bind_rows(
    `Summary meta-analysis` = all_res_mean,
    `Moderator analysis` = all_res_mod,
    .id = "Specification"
  ) %>%
  mutate(
    Specification = factor(Specification, levels = c("Summary meta-analysis","Moderator analysis")),
    across(c(Est, CI_lo, CI_hi), ~ case_when(
      param == "gamma" ~ exp(.x / 2), 
      param %in% c("zeta1","zeta2") ~ exp(.x),
      TRUE ~ .x
    )),
    param = recode(param, 
                   beta = "$\\beta_0$", 
                   `beta_(Intercept)` = "$\\beta_0$",
                   beta_outcome_type_author = "$\\beta_1$",
                   gamma = "$\\tau$", 
                   zeta1 = "$\\lambda_1$", 
                   zeta2 = "$\\lambda_2$"),
  )

all_res_table <- 
  all_res %>%
  mutate(
    Est_SE = paste0(formatC(Est, format = "f", digits = 2), " (",formatC(SE, format = "f", digits = 2),")"),
    CI = paste0("[", formatC(CI_lo, format = "f", digits = 2),", ", formatC(CI_hi, format = "f", digits = 2), "]")
  ) %>%
  select(Specification, Model, param, Est_SE, CI) %>%
  pivot_wider(names_from = Model, values_from = c(Est_SE, CI), names_vary = "slowest")

library(kableExtra)
options(knitr.kable.NA = '')

Specification_group <- table(all_res_table$Specification)

all_res_table %>%
  select(-Specification) %>%
  kbl(
    caption = "Selection model parameter estimates fit to science intervention effects from Taylor et al. (2018)",
    col.names = c("Parameter", rep(c("Est. (SE)", "95\\% CI"), times = 3)),
    booktabs = TRUE,
    escape = FALSE,
    table.attr = "tb"
  ) %>%
  kable_styling() %>%
  add_header_above(c(" ", "Beta density" = 2, "One-step" = 2, "Two-step" = 2)) %>%
  pack_rows(index = Specification_group) %>%
  footnote(
    general = c("Est. = estimate; SE = cluster-robust standard error; CI = cluster-robust confidence interval.")
  )
```


The upper panel of Table \@ref(tab:science-learning-res) reports parameter estimates from all three models, along with cluster-robust standard errors and 95% confidence intervals.
Across the three selection models, the estimated average effect sizes are all positive and significant, but they vary in magnitude and interpretation. Compared to the unadjusted model, the average adjusted effect is 25% smaller when using the beta-density selection model ($ES$ = `r round(sci_adj_beta_mean$est$Est[sci_adj_beta_mean$est$param=="beta"], 3)`), versus 32% larger when using the single-step model ($ES$ = `r round(sci_adj_step3_mean$est$Est[sci_adj_step3_mean$est$param=="beta"], 3)`) and 12% larger when using the two-step selection model ($ES$ = `r round(sci_adj_step4_mean$est$Est[sci_adj_step4_mean$est$param=="beta"], 3)`).
These differences are due to differences in the form of the selection curve estimated from each model specification, as depicted in figure \@ref(fig:science-selection-curves).
The beta-density model estimates of $\lambda_1$ and $\lambda_2$ imply that positive but non-significant results are slightly more likely to be reported compared to affirmative results, but that negative effects are increasingly less likely to be be reported.
On balance, this leads to an adjusted average effect size estimate that is smaller than under the unadjusted random effects model.
In contrast, the step-function models both estimate that non-significant results are more likely to be reported compared to affirmative results, leading to upward adjustment in the average effect size.
This divergence illustrates how the continuous functional form of the beta-density model can capture nuanced reporting patterns---such as a smooth decline in the likelihood of reporting for increasingly negative results---that may be obscured by the discrete thresholds of a step-function model.

```{r science-selection-curves}
#| echo: false
#| fig.retina: 2
#| fig.width: 5
#| fig.height: 5.5
#| out.width: 75%
#| fig.cap: "Estimated selection functions based on beta density, one-step, and two-step selection models"
#| fig.pos: tb 

pvals <- seq(0.001, 0.999, .001)

selection_curves <- 
  bind_rows(
    beta = selection_wts(sci_adj_beta_mean, pvals = pvals),
    `one-step` = selection_wts(sci_adj_step3_mean, pvals = pvals),
    `two-step` = selection_wts(sci_adj_step4_mean, pvals = pvals),
    .id = "Model"
  )

ggplot(selection_curves) + 
  aes(p, wt, color = Model, fill = Model) + 
  geom_vline(xintercept = c(.025, .975), linetype = "dashed") + 
  geom_area(alpha = 0.5) + 
  facet_wrap(~ Model, ncol = 1) + 
  scale_x_continuous(
    limits = c(0,1), 
    expand = expansion(0,0), 
    transform = "asn",
    breaks = c(0,.025, .10, .25, .5, .75, .90, .975, 1)
  ) + 
  theme_light() + 
  labs(x = "p-value (one-sided)", y = "Selection weight") + 
  theme(legend.position = "none", strip.text = element_text(color = "black"))
```

A key advantage of selection models over other methods for diagnosing and adjusting for selective reporting bias is that they allow for inclusion of potential moderator variables as predictors of average effect size. This feature allows meta-analysts to investigate whether selective reporting bias varies across study characteristics or, conversely, whether suspected moderator effects persist after adjusting for selection.
Past work has demonstrated that evaluations of educational interventions tend to produce larger effects on assessments developed by study authors or developers of the intervention (i.e., non-independent groups) than on assessments developed by groups independent of the evaluation [@Wolf2023making].
We investigated whether this pattern holds in the BSCS Science Learning meta-analysis data, which includes an indicator for assessment type, equal to one for assessments developed by non-independent groups and equal to zero otherwise.

We reran all four models using assessment type as a moderator [@taylor2018science], with assessments developed by independent groups as the reference category.
Based on a random effects meta-regression without adjustment for selective reporting, assessments developed by independent groups produced an average effect size of `r formatC(sci_unadj_mod$beta[1], format = "f", digits = 2)`, 95% CI [`r formatC(sci_unadj_mod$ci.lb[1], format = "f", digits = 2)`, `r formatC(sci_unadj_mod$ci.ub[1], format = "f", digits = 2)`].
The average effect on assessments developed by non-independent groups was larger by `r formatC(sci_unadj_mod$beta[2], format = "f", digits = 2)` SD, 95% CI [`r formatC(sci_unadj_mod$ci.lb[2], format = "f", digits = 2)`, `r formatC(sci_unadj_mod$ci.ub[2], format = "f", digits = 2)`], which was not statistically distinct from zero $(p = `r format.pval(sci_unadj_mod$pval[2], digits = 3, eps = 1e-3)`)$. 
The unadjusted estimate of heterogeneity was $\tau = `r formatC(sqrt(sci_unadj_mod$tau2), format = "f", digits = 2)`$, just as in the summary meta-analysis.

The lower panel of Table \@ref(tab:science-learning-res) reports parameter estimates from the corresponding selection models that include assessment type as a predictor.
The $\beta_1$ coefficient estimates represent differences in average effects between non-independent and independent assessment developers, which were all non-significant and similar in magnitude to the difference based on the unadjusted model.
This suggests that the assessment-type effect is not merely an artifact of selective reporting in this dataset.
However, the selection models lead to different conclusions about the average effects on independently developed assessments.
The estimate from the beta-density model is not statistically distinct from zero and is smaller than the estimate from the unadjusted random effects meta-regression. 
In contrast, the estimated average effects from the step-function selection models are both statistically significant and larger than the estimate from the unadjusted model.
Selection parameter estimates are very similar to the estimates from the corresponding summary meta-analysis models.

The results of this application demonstrate that the choice of selection function---smooth versus discrete---can lead to different conclusions regarding the magnitude and significance of adjusted effects. The beta-density selection model’s ability to capture a continuous range of selection probabilities provides a flexible alternative to the step-wise form of selection assumed by the step-function selection model, particularly when reporting bias does not follow rigid significance thresholds. To investigate the performance of these models more systematically, we conducted simulations across a wide range of conditions, focusing on the comparative performance of the beta-density and step-function specifications and their robustness to misspecification of the selection function.